---
title: "Assignment 7"
author: "Mohammad Zahid Chowdhury"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Introuduction: For Assignment 7, I have selected three books, each with two authors. Initially, I have written the code for the HTML, XML, and JSON files in a text editor, saved them accordingly, and uploaded them to my GitHub repository. Then, I read the files in HTML, XML, and JSON formats directly from GitHub and obtained the output in a tabular format.


# Load the required packages and libraries:

```{r}

install.packages("xml2", repos = "https://cran.rstudio.com/")


library(xml2)      # For xml file
library(jsonlite)  # For JSON processing
library(rvest)     # For HTML processing

```



# Read the HTML file


```{r}

html_data <- read_html("https://raw.githubusercontent.com/zahid607/Assignment-7/refs/heads/main/books.html")

# Extract the table
books_table <- html_data %>%
  html_node("table") %>%
  html_table(fill = TRUE)

# Convert to a data frame
df_html <- as.data.frame(books_table)

# Print the data frame
print(df_html)



```


# Read the xml file:

```{r}

# Define the raw XML file URL
xml_url <- "https://raw.githubusercontent.com/zahid607/Assignment-7/main/books.xml"


xml_data <- read_xml(xml_url)

# Extract book nodes
books <- xml_find_all(xml_data, "//book")

# Convert to a data frame
df_xml <- data.frame(
  Title = xml_text(xml_find_first(books, "title")),
  Authors = sapply(books, function(book) {
    paste(xml_text(xml_find_all(book, "authors/author")), collapse = ", ")
  }),
  Year = as.numeric(xml_text(xml_find_first(books, "year"))),
  Publisher = xml_text(xml_find_first(books, "publisher")),
  stringsAsFactors = FALSE
)

# Print the data frame
print(df_xml)


```

# Read the Json file:

```{r}
json_data <- fromJSON("https://raw.githubusercontent.com/zahid607/Assignment-7/refs/heads/main/books.json")

df_json <- as.data.frame(json_data$books)

# Convert authors list to string
df_json$Authors <- sapply(df_json$authors, paste, collapse = ", ")
df_json$authors <- NULL  # Remove original authors list

print(df_json)

```


# Are the three data frames identical? 


```{r}

# Check if df_html and df_xml are identical
identical(df_html, df_xml)

# Check if df_html and df_json are identical
identical(df_html, df_json)

# Check if df_xml and df_json are identical
identical(df_xml, df_json)


```

# Conclusion: So, we can conclude that all files HTML, XML and JSON files are not identical.

